Fig3

### 2020-04-13 analysis/figure-3.Rmd
more correlations

plotcorrs <- function(whichtissue){

  x <- vsdhormones  %>%
    filter(tissue == whichtissue) %>%
    select(-sex, - tissue, - treatment, -samples, -bird_id, -moltbin) %>%
    correlate()
  print(fashion(x))

  p <- rplot(x, colors = c("#0571b0", "#92c5de", "#f7f7f7","#f7f7f7","#f7f7f7", "#f4a582", "#ca0020")) +
    theme_B3() +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = 1),
          axis.text = element_text(face = "italic")) +
    labs(subtitle = whichtissue)
  return(p)
}

a <- plotcorrs("hypothalamus") 
b <- plotcorrs("pituitary") + theme(axis.text.y = element_blank())
c <- plotcorrs("gonad") + theme(axis.text.y = element_blank())

plot_grid(a,b,c, nrow = 1, rel_widths = c(1.2,1,1))

>>>>

vsdhormoneshyp <- vsdhormones %>% filter(tissue == "hypothalamus" )
vsdhormonespit <- vsdhormones %>% filter(tissue == "pituitary" )
vsdhormonesgon <- vsdhormones %>% filter(tissue == "gonad" )

plotcorrs <- function(whichtissue, whichsex){

  x <- vsdhormones  %>%
    filter(tissue == whichtissue, 
           sex == whichsex) %>%
    select(-sex, - tissue, - treatment, -samples, -bird_id, -moltbin) %>%
    correlate()
  print(fashion(x))

  p <-rplot(x, colors = c("#0571b0", "#92c5de", "#f7f7f7","#f7f7f7","#f7f7f7", "#f4a582", "#ca0020")) +
    theme_B3() +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = 1),
          axis.text = element_text(face = "italic")) +
    labs(subtitle = whichtissue)
  return(p)
}

a <- plotcorrs("hypothalamus", "female") + theme(legend.position = "none")
b <- plotcorrs("pituitary", "female") + theme(axis.text.y = element_blank()) + theme(legend.position = "none")
c <- plotcorrs("gonad", "female") + theme(axis.text.y = element_blank()) + theme(legend.position = "none")

d <- plotcorrs("hypothalamus", "male") 
e <- plotcorrs("pituitary", "male") + theme(axis.text.y = element_blank())
f <- plotcorrs("gonad", "male") + theme(axis.text.y = element_blank())

plot_grid(a,b,c, d,e,f, nrow = 2, rel_widths = c(1.2,1,1), rel_heights = c(1,1.2))

plotspecificcorrs <- function(df, myx, myy, myxlab, myylab){
  p <- df %>%
    mutate(tissue = factor(tissue, levels = tissuelevel)) %>%
    ggplot(aes(x = myx, y = myy)) +
    geom_point(aes(color = treatment)) +
    geom_smooth(method = "lm", aes(color = sex)) +
    facet_wrap(~sex, scales = "free", nrow = 2) +
    scale_color_manual(values = allcolors) +
    labs(x = myxlab, y = myylab) +
    theme_B3() +
    theme(legend.position = "none",
          axis.title = element_text(face = "italic"))
  return(p)
}

a <- plotspecificcorrs(vsdhormoneshyp, vsdhormoneshyp$FSHB, vsdhormoneshyp$PRL, "FSHB", "PRL") + labs(subtitle = "Hypothalamus")
b <- plotspecificcorrs(vsdhormonespit, vsdhormonespit$prolactin, vsdhormonespit$PRL, "circulating prolactin", "PRL") +
  theme(axis.title.x = element_text(face = "plain")) + labs(subtitle = "Pituitary")
c <- plotspecificcorrs(vsdhormonesgon, vsdhormonesgon$ESR1, vsdhormonesgon$PGR, "ESR1", "PGR")  + labs(subtitle = "Gonads")

plot_grid(a,b,c,nrow = 1, labels = "auto", label_size = 8)
```
